### 2020-05-29 README.Rmd
[docs] Update README

# Please put your title here to include it in the file below.
Title <- "An R-based framework for conducting parametric analysis on building energy models"
```

# eplusr + epluspar

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r
> Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at
> <https://doi.org/xxx/xxx>

@@

@@

>>>>

# Please put your title here to include it in the file below.
Title <- "A framework for integrating building energy simulation and data-driven analytics"
Author <- "Hongyuan Jia and Adrian Chong"
Journal <- "Energy and Buildings"
```

# eplusr framework

@@

> `r Author`, (2020). _`r Title`_. `r Journal` <https://doi.org/xxx/xxx>

@@

> `r Author`, (2020). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> `r Author`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

**(a) Option 1: Download the compiled draft PDF**

The latest compiled draft PDF can be downloaded from the `Artifacts`.

```{r, echo = FALSE}
knitr::include_graphics(here::here("figures/artifact.png"))
```

**(b) Option 2: Download the compendium and compile the PDF**

@@

The PDF can be compiled via:

```{r, eval = FALSE}
rmarkdown::render('vignettes/paper.Rmd')
```
